Correlations between PTBP at different resolutions

### 2020-07-03 Scripts_for_results/07_creating_distance_to_chipseq.Rmd
updated results

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

@@

>>>>

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(2:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

@@

# Combining ARROWHEAD & PEAKACHU for Figure 5D

```{r}
pred_v_called_df_a$BoundReg <- factor(pred_v_called_df_a$BoundReg, levels=c("ARROWHEAD","preciseTAD"))
pred_v_called_df_p$BoundReg <- factor(pred_v_called_df_p$BoundReg, levels=c("PEAKACHU","preciseTAD"))

a <- ggplot(pred_v_called_df_a[which(pred_v_called_df_a$Annotation=="CTCF"),], aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  +   
    stat_boxplot(geom ='errorbar', width = 0.2) + 
    geom_boxplot(outlier.shape = NA) +
    geom_signif(test = "wilcox.test", 
                comparisons = list(c("preciseTAD","ARROWHEAD")),
                vjust = 0,
                textsize = 4,
                size = .5,
                #step_increase = .5,
                color="black") +
    theme_minimal()+
    theme_bw()+
    ylab("Log2 Distance to CTCF")+
    xlab("") +
    scale_fill_manual(values=c("blue",
                               "forestgreen"))+
    scale_color_manual(values=c("blue",
                                "forestgreen")) +
    guides(color=FALSE, fill=FALSE)+
    theme(axis.text.x = element_text(size=10,
                                     angle = 45,
                                     hjust = 1),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          strip.text.x = element_text(size = 10),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=10),
          legend.title=element_text(size=15),
          plot.title = element_text(size=15),
          legend.position = "bottom")

b <- ggplot(pred_v_called_df_p[which(pred_v_called_df_p$Annotation=="CTCF"),], aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  +   
    stat_boxplot(geom ='errorbar', width = 0.2) + 
    geom_boxplot(outlier.shape = NA) +
    geom_signif(test = "wilcox.test", 
                comparisons = list(c("preciseTAD","PEAKACHU")),
                vjust = 0,
                textsize = 4,
                size = .5,
                #step_increase = .5,
                color="black") +
    theme_minimal()+
    theme_bw()+
    ylab("")+
    xlab("") +
    scale_fill_manual(values=c("red",
                               "forestgreen"))+
    scale_color_manual(values=c("red",
                                "forestgreen")) +
    guides(color=FALSE, fill=FALSE)+
    theme(axis.text.x = element_text(size=10,
                                     angle = 45,
                                     hjust = 1),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          strip.text.x = element_text(size = 10),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=10),
          legend.title=element_text(size=15),
          plot.title = element_text(size=15),
          legend.position = "bottom")

ggarrange(a,b,ncol = 2)
```

### 2020-07-03 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.Rmd
edits
updated results

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrf.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

@@

## Running TADrf and preciseTAD

```{r}
tadModel <- TADrf(bounds.GR=bounds.GR,
                  resolution=5000,
                  genomicElements.GR=genomicElements.GR,
                  featureType="distance",
                  resampling="rus",
                  trainCHR=paste0("CHR", c(1:8,10:22)),
                  predictCHR=NULL,
                  cvFolds=3,
                  ntrees=100,
                  cvMetric="Accuracy",
                  verbose=TRUE,
                  seed=123,
                  model=TRUE,
                  importances=TRUE,
                  performances=FALSE)

bounds.GR <- extract_boundaries_func(domains.mat=domains, 
                                     preprocess=FALSE, 
                                     #CHR="CHR22", 
                                     CHR="CHR21", 
                                     resolution=5000)

pt <- preciseTAD(bounds.GR=bounds.GR,
                      genomicElements.GR=genomicElements.GR,
                      featureType="distance",
                      #CHR="CHR22",
                      CHR="CHR21",
                      #chromCoords=list(17389000,18011000),
                      chromCoords=list(15150000,17270000),
                      tadModel=tadModel[[1]],
                      threshold=1.0,
                      flank=NULL,
                      verbose=TRUE,
                      seed=123,
                      parallel=FALSE,
                      cores=NULL,
                      splits=NULL,
                      method.Dist="euclidean",
                      DBSCAN=TRUE,
                      DBSCAN_params=list(5000,3), #or list(10000,3)
                      method.Clust=NULL,
                      PTBR=TRUE,
                      CLARA=FALSE,
                      samples=100)

@@

```{r}
getChrLength <- function(genome = "BSgenome.Hsapiens.UCSC.hg19"){
  g <- getBSgenome(genome, masked=FALSE)
  data.frame(chrom=1:24, length=seqlengths(g)[1:24])
}
.chrAsNum <- function(tbl){
  tbl$chrom <- gsub("chr", "", tbl$chrom)
  tbl$chrom[tbl$chrom=="X"] <- 23
  tbl$chrom[tbl$chrom=="Y"] <- 24
  tbl$chrom <- as.numeric(tbl$chrom)
  tbl[order(tbl$chrom),]
}
getCentromeres <- function( genome="hg19" ){
  mySession <- try(browserSession("UCSC"), silent=TRUE)
  # In case of failure, try another mirror
  if(inherits(mySession, "try-error"))
    mySession <- browserSession("UCSC",
                                url="http://genome-euro.ucsc.edu/cgi-bin/")
  genome(mySession) <- genome
  obj <- ucscTableQuery(mySession, table="gap")
  tbl <- getTable(obj)
  tbl <- tbl[tbl$type=="centromere", c("chrom", "chromStart", "chromEnd")]
  colnames(tbl)[2:3] <- c("centromerStart", "centromerEnd")
  .chrAsNum(tbl)
}
makeHg19 <- function(){
  tbl <- merge(getChrLength(), getCentromeres(), by="chrom")
  cumlen <- c(0, cumsum(as.numeric(tbl$length))[-nrow(tbl)])
  cbind.data.frame(tbl, cumlen=cumlen)    
}
hg19 <- makeHg19()
hg19$chrom <- paste0("CHR",hg19$chrom)

#seqDataTest <- c(17389000:18011000)
#seqDataTest <- c(25745000:26176000)
seqDataTest <- c(15150000:17270000)

#CHR="CHR22"
CHR="CHR21"

@@

predprobdata <- data.frame(#basenum=c(17389000:18011000),
                           basenum=c(15150000:17270000),
                           prob=predictions)
predprobdata$predicted <- ifelse(predprobdata$basenum %in% start(pt[[2]]), "Yes", "No")
predprobdata$called <- ifelse(predprobdata$basenum %in% start(pt[[3]]), "Yes", "No")

@@

ggplot() + 
  geom_line(data=predprobdata, aes(x=basenum, y=prob), 
            color='black',
            size=1)+
  #geom_vline(data=predicteddata, aes(xintercept=basenum, 
  #                                   color="red"),
  #           size=.5,
  #           show.legend = TRUE)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
                                      color="forestgreen"),
             size=1,
             show.legend = TRUE)+
  #annotate(geom = "segment",x = 15492234, xend = 15519798,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  #annotate(geom = "segment",x = 15635994, xend = 15792137,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  #annotate(geom = "segment",x = 16147181, xend = 16244962,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  #annotate(geom = "segment",x = 16845543, xend = 16958034,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  xlab("Base Pair Coordinate") +
  ylab("Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "forestgreen"),
                     labels = c("ARROWHEAD",
                                "preciseTAD"))+
  scale_y_continuous(breaks=c(0,.5,1), limits=c(0,1))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

ptbrdata <- data.frame(basenum=c(15770000:15780000))

>>>>

source("Z:/TAD_data_analysis/functions_for_R_package/createTADdata.R")
source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrandomForest.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

@@

## Creating data matrix

```{r}
tadData <- createTADdata(bounds.GR=bounds.GR,
                         resolution=5000,
                         genomicElements.GR=genomicElements.GR,
                         featureType="distance",
                         resampling="rus",
                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))=="CHR22")],
                         predictCHR=NULL,
                         seed=123)
```

## Running TADrandomForest

```{r}
tadModel <- TADrandomForest(trainData=tadData[[1]],
                            testData=NULL,
                            tuneParams=list(mtry=2,
                                            ntree=500,
                                            nodesize=1),
                            cvFolds=3,
                            cvMetric="Accuracy",
                            verbose=TRUE,
                            seed=123,
                            model=TRUE,
                            importances=TRUE,
                            impMeasure="MDA",
                            performances=FALSE)
```

## Running preciseTAD

```{r}
bounds.GR <- extract_boundaries_func(domains.mat=domains, 
                                     preprocess=FALSE, 
                                     CHR="CHR22", 
                                     resolution=5000)

pt <- preciseTAD(bounds.GR=bounds.GR,
                      genomicElements.GR=genomicElements.GR,
                      featureType="distance",
                      CHR="CHR22",
                      chromCoords=list(17000000,19000000),
                      tadModel=tadModel[[1]],
                      threshold=1.0,
                      flank=NULL,
                      verbose=TRUE,
                      seed=123,
                      parallel=FALSE,
                      cores=NULL,
                      splits=NULL,
                      method.Dist="euclidean",
                      DBSCAN=TRUE,
                      DBSCAN_params=list(5000,3), 
                      method.Clust=NULL,
                      PTBR=TRUE,
                      CLARA=FALSE,
                      samples=100)

saveRDS(pt, "C:/Users/stili/Downloads/pt_chr21_15150000_17270000")
```

@@

```{r}
tadModel <- readRDS("Z:/TAD_data_analysis/miscellaneous/tadModel.rds")
pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")

getChrLength <- function(genome = "BSgenome.Hsapiens.UCSC.hg19"){
  g <- getBSgenome(genome, masked=FALSE)
  data.frame(chrom=1:24, length=seqlengths(g)[1:24])
}
.chrAsNum <- function(tbl){
  tbl$chrom <- gsub("chr", "", tbl$chrom)
  tbl$chrom[tbl$chrom=="X"] <- 23
  tbl$chrom[tbl$chrom=="Y"] <- 24
  tbl$chrom <- as.numeric(tbl$chrom)
  tbl[order(tbl$chrom),]
}
getCentromeres <- function( genome="hg19" ){
  mySession <- try(browserSession("UCSC"), silent=TRUE)
  # In case of failure, try another mirror
  if(inherits(mySession, "try-error"))
    mySession <- browserSession("UCSC",
                                url="http://genome-euro.ucsc.edu/cgi-bin/")
  genome(mySession) <- genome
  obj <- ucscTableQuery(mySession, table="gap")
  tbl <- getTable(obj)
  tbl <- tbl[tbl$type=="centromere", c("chrom", "chromStart", "chromEnd")]
  colnames(tbl)[2:3] <- c("centromerStart", "centromerEnd")
  .chrAsNum(tbl)
}
makeHg19 <- function(){
  tbl <- merge(getChrLength(), getCentromeres(), by="chrom")
  cumlen <- c(0, cumsum(as.numeric(tbl$length))[-nrow(tbl)])
  cbind.data.frame(tbl, cumlen=cumlen)    
}
hg19 <- makeHg19()
hg19$chrom <- paste0("CHR",hg19$chrom)

#seqDataTest <- c(17389000:18011000)
#seqDataTest <- c(25745000:26176000)
#seqDataTest <- c(15150000:17270000)
seqDataTest <- c(70595000:71525000)

#CHR="CHR22"
#CHR="CHR21"
CHR="CHR1"

@@

predprobdata <- data.frame(#basenum=c(17389000:18011000),
                           #basenum=c(15150000:17270000),
                           basenum=c(70595000:71525000),
                           prob=predictions)
predprobdata$predicted <- ifelse(predprobdata$basenum %in% start(pt[[2]]), "Yes", "No")
predprobdata$called <- ifelse(predprobdata$basenum %in% start(pt[[3]]), "Yes", "No")

@@

ggplot() + 
  geom_line(data=predprobdata, aes(x=basenum, y=prob), 
            color='black',
            size=1)+
  #geom_vline(data=predicteddata, aes(xintercept=basenum, 
  #                                   color="red"),
  #           size=.5,
  #           show.legend = TRUE)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=1.5,
             show.legend = TRUE)+
  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
                                      color="forestgreen"),
             size=1.5,
             show.legend = TRUE)+
  #annotate(geom = "segment",x = 15492234, xend = 15519798,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  #annotate(geom = "segment",x = 15635994, xend = 15792137,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  #annotate(geom = "segment",x = 16147181, xend = 16244962,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  #annotate(geom = "segment",x = 16845543, xend = 16958034,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  xlab("Base Pair Coordinate") +
  ylab("Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "forestgreen"),
                     labels = c("ARROWHEAD",
                                "preciseTAD"))+
  scale_y_continuous(breaks=c(0,.5,1), limits=c(0,1))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

#ptbrdata <- data.frame(basenum=c(15770000:15780000))
ptbrdata <- data.frame(basenum=c(70900000:70950000))

### 2020-07-03 Scripts_for_results/11_correlations_across_resolutions.Rmd
updated results

```{r}
jaccard_mod <- function (query, reference, restrict = NULL, modified=TRUE) {
  if(isTRUE(modified)){
    int = sum(width(intersect(query, reference)))
    minunion = min(sum(as.numeric(width(intersect(query, reference)))),sum(as.numeric(width(union(query, reference)))))
    res = int/minunion
  }else{
    res = sum(width(intersect(query, reference)))/sum(as.numeric(width(union(query, reference)))) 
  }
  return(res)
}
```

>>>>

```{r}
jaccard_mod <- function (query, reference, restrict = NULL, modified=FALSE) {
  if(isTRUE(modified)){
    int = sum(width(GenomicRanges::intersect(query, reference)))
    minunion = min(sum(as.numeric(width(GenomicRanges::intersect(query, reference)))),sum(as.numeric(width(GenomicRanges::union(query, reference)))))
    res = int/minunion
  }else{
    res = sum(width(GenomicRanges::intersect(query, reference)))/sum(as.numeric(width(GenomicRanges::union(query, reference)))) 
  }
  return(res)
}

genomicCorr.jaccard = function(query, reference, restrict = NULL) {
	if(is.null(restrict)) {
		res = sum(width(GenomicRanges::intersect(query, reference))) / sum(as.numeric(width(GenomicRanges::union(query, reference))))
	} else {
		gr1 = GenomicRanges::intersect(query, reference)
		gr1 = GenomicRanges::intersect(gr1, restrict)

		gr2 = GenomicRanges::union(query, reference)
		gr2 = GenomicRanges::intersect(gr2, restrict)
		res = sum(width(gr1)) / sum(width(gr2))
	}
	return(res)
}
```
